Certified Desugaring of Javascript Programs using Coq

### 2016-12-14 paper/paper.tex
tiny comment

\usepackage{todonotes}
\newcommand{\as}[1]{\todo[color=green]{#1}}
\newcommand{\asi}[1]{\todo[color=green,inline]{#1}}
\newcommand{\mm}[1]{\todo[color=blue]{#1}}
\newcommand{\mmi}[1]{\todo[color=blue,inline]{#1}}

@@

To reduce the complexity of the task, we are currently working
only on proving \lambdajs correct with respect to JSCert,
i.e., that if the \lambdajs program successfully terminates,
then its result matches the result given by JSCert. We are also
restricting our attention to ECMAScript strict mode, proving the
correctness of non-strict features only when it is convenient.
\asi{How difficult would it be to prove the other direction (if we have a
  derivation in JSCert, then we have one in \lambdajs?)}
\mmi{It would require inverting the JSCert semantic judgments.
  Is this working now? I remember Petar trying to do this.}

>>>>

\usepackage{todonotes}

\definecolor{aliceblue}{rgb}{0.94, 0.97, 1.0}

\newcommand{\as}[1]{\todo[color=green]{#1}}
\newcommand{\asi}[1]{\todo[color=green,inline]{#1}}
\newcommand{\mm}[1]{\todo[color=aliceblue]{#1}}
\newcommand{\mmi}[1]{\todo[color=aliceblue,inline]{#1}}

@@

To reduce the complexity of the task, we are currently working
only on proving \lambdajs correct with respect to JSCert,
i.e., that if the \lambdajs program successfully terminates,
then its result matches the result given by JSCert. We are also
restricting our attention to ECMAScript strict mode, proving the
correctness of non-strict features only when it is convenient.
\asi{We should have a sentence like ``Proving the other direction requires doing
  an inversion of the full JSCert semantics. Unfortunately, the techniques we
  have used (see Section $\ldots$) do not scale to semantics of that size.'' }
